---
title: "WEEK_3 Report"
description: |
  First try to predict sale price with AmesHousing data
author:
  - name: sonsungman
    url: https://sonsungman.github.io/SKKU-Preditive.m/
date: 03-15-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: true
    draft: true
---
```{r setup, include=FALSE}
library(AmesHousing) ; library(tidyverse) ;library(purrr) ; library(magrittr)
```


### Introduction


The aim of this report is regression modeling for sales price forecasting.


Last week, I explored and visualized Ames Housing data to find independent variables appropriate for home sales price prediction modeling.


Among the three problem (regression problem, classification problems, and clustering problem) presented in ISL, sales price prediction corresponds to regression problem.


So first, I review the contents of the previous report again. Second, I rethink feedback and peer reviews on my data analysis report and consider some new facts. Third, I visualize data that can support previous discussions. Finally, I build a multi-regression model to predict the sales price based on the previous results.


### Review of previous Report


In the last report, I was able to identify some variables that could affect house prices and fact through data exploration and visualization.


 - The presence of swimming pools and pavement conditions on the streets are insufficient to affect housing prices.
 
 
 - 'Overall Qual' column (Rates the overall material and finish of the house) is a positive correlation with house price.
 
 
 - The larger the size of the house, of course the higher the price of the house, but the size of the house does not seem to be a decisive factor.
 
 
 - The capacity of a garage in a house appears to be a variable that affects house price.
 
 
 - The timing of house construction or remodeling will affect house prices.
 
 
### Peer review and feedback from the Professor Lee


 - There is no reason not to use house data built or remodeled before 1980 for modeling. Therefore, there may be a way to combine pre-1980 data into the 1980.
 
 
 - The variable regarding the capacity of the garage may be correlated with the Lot Area variable. Therefore, it is necessary to rethink the consideration of both variables in modeling.
 
 
 - The neighborhood around the house affects the price.
 

### Building a multi-regression model

Based on the year of architecture or remodeling, data is divided before and after 1980 and analyzed using multiple regression analyses, respectively.


```{r}
## Data divided

  data1<- ames_raw %>%
    filter(`Year Remod/Add` <= 1980)

  data2<- ames_raw %>%
    filter(`Year Remod/Add` > 1980)
  
```


As an independent variable of the model, I use `Lot Area`, `Overall Qual`,and `Garage Cars`. It was modeled by dividing the housing according to the area in which it was located.


```{r}
  nrow(data1)

  data1 %>% 
      group_by(Neighborhood) %>%
      summarize(count = n())  
```

```{r}


  nested_df<-data1 %>% 
    group_by(Neighborhood) %>%
    nest() %>% ungroup(Neighborhood)
    
  nested_df %>%
   mutate(model = map(data, ~lm(SalePrice ~ `Lot Area` + `Overall Qual` + `Garage Cars` , data=.))) %>%
    transmute(Neighborhood, map_df(model, ~summary(.)$coefficients[,1]))

  
```


After multiple regression analyses based on the three independent variables mentioned above with house data prior to 1980, the estimated parameters were presented by neighborhood.


```{r}
  nrow(data2)

  data2 %>% 
      group_by(Neighborhood) %>%
      summarize(count = n())  
```


```{r}

  nested_df2<-data2 %>% 
    group_by(Neighborhood) %>%
    nest() %>% ungroup(Neighborhood)

nested_df2 %>%
   mutate(model = map(data, ~lm(SalePrice ~ `Lot Area` + `Overall Qual` + `Garage Cars` , data=.))) ## %>%
  ## 오류 발생  transmute(Neighborhood, map_df(model, ~summary(.)$coefficients[,1]))

```
