---
title: "WEEK_11 Report"
description: |
  HW 2 Solution
author:
  - name: sonsungman
    url: https://sonsungman.github.io/SKKU-Preditive.m/
date: 05-13-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: true
    draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")
library(purrr) ; library(magrittr) ; library(MASS)
```

```{r load_lib, include=FALSE}
library(tidymodels)
library(tidyverse)
library(magrittr)
library(skimr)
library(knitr)
library(glmnet)
library(caret)
theme_set(theme_bw())
```

## 1. Exponential family

### 1) Bernulli

Taking the log and then the exponential,

$$
\begin{aligned}
    f(y;p) &= p^{y}(1-p)^{1-y} \\
    &= exp[yln(p) + (1-y)ln(1-p)] \\
    &= exp[yln(\frac{p}{1-p}) + ln(1-p)] \\
\end{aligned}
$$

$\theta = ln(\frac{p}{1-p})$ is natural or canonical parameter.

$a(\phi) = 1$

$b(\theta) = -ln(\frac{1}{1+exp(\theta)})$

$c(y, \phi) = 0$

### 2) Poisson

Taking the log and then the exponential,

$$
  \begin{aligned}
    f(y;\theta,\phi) &=\frac{\lambda^{y}e^{-\lambda}}{y!} \\
    &= exp[ln(\frac{\lambda^{y}e^{-\lambda}}{y!})] \\
    &= exp[ ln(\lambda^{y}e^{-\lambda}) - ln(y!)] \\
    &= exp[yln(\lambda) - \lambda - ln(y!)] \\
  \end{aligned}
$$

$\theta = ln(\lambda)$ is natural or canonical parameter.

$a(\phi) = 1$

$b(\theta) = e^{\theta}$

$c(y, \phi) = -ln(y!)$

### 3) Verify the logit link for the logistic regression and the log link for the poisson regression are the canonical link functions.


For logistic regression, 
$$
  \begin{aligned}
    E(y_{i}) &= \mu_{i} = p \\
    g(\mu_{i}) &= logit(\mu_{i}) = ln(\frac{p}{1-p}) = \theta
  \end{aligned}
$$
For poisson regression, 
$$
  \begin{aligned}
    E(y_{i}) &= \mu_{i} = \lambda \\
    g(\mu_{i}) &= log(\mu_{i}) = ln(\lambda) = \theta
  \end{aligned}
$$

## 2. Maximum Likelihood Estimator of Poisson Regression

### 1) Calculate the coefficients by using the following code


```{r message=FALSE}
example_data <- read_csv("example_data.csv", col_names = FALSE) 
colnames(example_data) <- c("Policy", "Policy.Years", "Gender", "Territory","Claims") 
example_data 

 dmy <- dummyVars(~., data = example_data)
  example_data_pre<- as.tibble(predict(dmy, newdata = example_data))

    example_data_pre

```

```{r}
  Result<-glm(Claims ~ Gender + Territory, family = poisson(link=log), data = example_data)

Result2<-glm(Claims ~   GenderF + GenderM + TerritoryWest + TerritoryEast, family = poisson(link=log), data = example_data_pre)

  Result$coefficients
  Result2$coefficients
```

### 2) Find the coefficients of Poisson regression above using an user define R function via gradient descent algorithm. Your answer must include the following steps:
- Define Likelihood and Loglikelihood function.
- Calculate gradient of Loglikelihood function with repect to $\beta$.


a) Define Likelihood and Loglikelihood function

$$
  \begin{aligned}
    Y_{i} &\sim {\sf Poisson}(\lambda_{i}) \\
    ln(\lambda_{i}) &= \beta_{0} + \beta_{1}x_{i1} + \beta_{2}x_{i2}
  \end{aligned}
$$
$Y_{i}$ is Claims.

$x_{i1}$ is Gender.

$x_{i2}$ is Territory.

$$
  \begin{aligned}
    L(\beta_{0},\beta_{1},\beta_{2}) &= \prod_{i = 1}^{12} \frac{\lambda_{i}^{Y_{i}}e^{-\lambda_{i}}}{Y_{i}!} \\
    l(\beta_{0},\beta_{1},\beta_{2}) &= \sum_{i = 1}^{12} Y_{i}ln\lambda_{i} - \lambda_{i} - lnY_{i}! \\
    &= \sum_{i = 1}^{12} Y_{i}(\sum_{j = 0}^{2}\beta_{j}x_{ij})-e^{\sum_{j = 0}^{2}\beta_{j}x_{ij}}-lnY_{i}!
  \end{aligned}
$$


b) Calculate gradient of Loglikelihood function with repect to $\beta$.

```{r}
beta<-rnorm(3)
nll <- function(beta){
    y <- example_data_pre$Claims
    ln_lambda <- matrix(cbind(1, example_data_pre$GenderM,
                          example_data_pre$TerritoryWest),
         ncol = 3) %*% beta
    
    -sum(y*ln_lambda-exp(ln_lambda)-log(factorial(y)))
}

nll(beta)
```
```{r}
beta<-rnorm(3)
grad_nll <- function(beta){
    y <- example_data_pre$Claims
    ln_lambda <- matrix(cbind(1, example_data_pre$GenderM,
                          example_data_pre$TerritoryWest),
         ncol = 3) %*% beta
    
  -colSums(matrix(cbind(1, example_data_pre$GenderM,
                          example_data_pre$TerritoryWest),
         ncol = 3)*as.vector(y - exp(ln_lambda)))
}

grad_nll(beta)
```

```{r}
  set.seed(2021)
beta <- rnorm(3)
iter_n <- 1
improve <- 1
conv_threshold <- 1e-5
max_n <- 10000
result <- matrix(0, nrow = max_n, ncol = 3)
while ((improve > conv_threshold) & (iter_n <= max_n)) {
    beta_new <- beta - 0.001 * grad_nll(beta)
    improve <- abs(nll(beta) - nll(beta_new))
    result[iter_n,] <- beta_new
    beta <- beta_new
    iter_n <- iter_n + 1
}

iter_n ; result[1798,] ; result[1799,]

```

