---
title: "WEEK_12 Report"
description: |
  Deeping learning with Torch
author:
  - name: sonsungman
    url: https://sonsungman.github.io/SKKU-Preditive.m/
date: 05-20-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: true
    draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")
library(purrr) ; library(magrittr) ; library(MASS)
```

```{r load_lib, include=FALSE}
library(tidymodels)
library(tidyverse)
library(magrittr)
library(skimr)
library(knitr)
library(kernlab)
theme_set(theme_bw())
```

### Introduction

The use of neural networks, generally referred to as 'Deep Learning', in the Actuarial Science is increasing.
Claim reserving, non-life pricing, mortality modelling, and telematics are the examples. In this report, Using a package called torch, I try to use deep learning in R.

***

A list of the books I have referenced to produce this report is shown below.

> -  AI in Actuarial Science, Ronald Richman(2018)
> -  https://deeplearning-playbook.netlify.app/ 딥러닝 공략집, 슬기로운 통계 생활(2021)


***
